The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-09-07 manuscript.Rmd
[fix #62] calculate set sizes from data

A higher proportion of the species included in the regional list for the GOM are captured in biodiversity databases than for the PNW. While `r format_output((3890 + 2663 + 1025 + 316 + 102 + 49 )/n_distinct(total_gom_records$worms_valid_name) * 100)`%  of the species included in the checklist for the GOM have records in at least one of the biodiversity database (Fig. \@ref(fig:database-coverage)A), only `r format_output((352 + 292 + 281 + 235 + 76 + 38)/n_distinct(total_pnw_records$worms_valid_name)*100)`% do for the PNW  (Fig. \@ref(fig:database-coverage)B). Additionally, a higher proportion of species occur in the biodiversity databases but are not included in the regional checklist for the GOM compared with the PNW (GOM: `r format_output((1253 + 848 + 556 + 216 + 190 + 124) / n_distinct(total_gom_records$worms_valid_name)*100)`%, $n =$ `r format(n_distinct(total_gom_records$worms_valid_name), big.mark=",")`; PNW:
`r format_output( (281 + 151 + 145 + 80 + 78 + 45) / n_distinct(total_pnw_records$worms_valid_name)*100)`%, $n =$ `r format(n_distinct(total_pnw_records$worms_valid_name), big.mark=",")`).

>>>>

```{r}
set_size_gom <- function(...)
    set_size_with_checklist(..., d = remake::fetch("total_gom_species"))
set_size_pnw <- function(...)
    set_size_with_checklist(..., d = remake::fetch("total_pnw_species"))
```

A higher proportion of the species included in the regional list for the GOM are captured in biodiversity databases than for the PNW. While `r format_output(set_size_gom("checklist","idigbio","obis")/n_distinct(total_gom_records$worms_valid_name) * 100)`%  of the species included in the checklist for the GOM have records in at least one of the biodiversity database (Fig. \@ref(fig:database-coverage)A), only `r format_output(set_size_pnw("checklist","idigbio","obis")/n_distinct(total_pnw_records$worms_valid_name)*100)`% do for the PNW  (Fig. \@ref(fig:database-coverage)B). Additionally, a higher proportion of species occur in the biodiversity databases but are not included in the regional checklist for the GOM compared with the PNW (GOM: `r format_output(set_size_gom("checklist","idigbio","obis",include_checklist=FALSE) / n_distinct(total_gom_records$worms_valid_name)*100)`%, $n =$ `r format(n_distinct(total_gom_records$worms_valid_name), big.mark=",")`; PNW:
`r format_output( set_size_pnw("checklist","idigbio","obis",include_checklist=FALSE) / n_distinct(total_pnw_records$worms_valid_name)*100)`%, $n =$ `r format(n_distinct(total_pnw_records$worms_valid_name), big.mark=",")`).
